Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-13 alloscore_manuscript/alloscore-application.Rnw
a few cosmetic changes

\usepackage{amsmath, amsfonts, amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{cases}
\usepackage{caption}
\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{supplement}

\DeclareMathOperator*{\argmin}{argmin}

@@

An additional limitation of the current work and opportunity for further investigation is to more carefully evaluate whether a forecast adds value to existing decision making processes.
In the context of allocation-based decisions, standard procedures might involve extrapolating need based on a current observed data (similar to the `baseline' model presented above), with or without adjustments based on other political or real-world considerations.
For example, in many settings public health stakeholders will synthesize multiple sources of information, e.g. real-time data from a wide variety of quantitative and qualitative sources coupled with expert judgment based on a situational understanding of past and current experience.
The allocation score presented in this work assesses the optimality of the allocation with reference an omniscient view of the future captured by the oracle.
However, what we care about is whether a given forecast adds useful information to an existing decision-making process.
While the scoring procedures as presented do not directly address this question, they could be modified (say, by comparison to a `baseline` model) to quantify the benefit -if any- of using a forecast to inform a specific decision.

We see this work as an initial overture for what we hope will grow to be a large, collaborative body of work more closely coupling applied epidemiological forecasting with public health decision making.
We note that a few papers have begun exploring similar linkages as described in the literature review \textendash but we see much room for additional work in this area.
In some situations, individual or ensemble models could be developed to optimize scores that are attuned to a particular decision making setting.
This area is also largely unexplored in the realm of public health to date, with some initial methodological development in econometrics \citep{loaiza-maya_focused_2021}.

>>>>

\usepackage{amsmath, amsfonts, amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{cases}
\usepackage{caption}
\usepackage{xr-hyper}
\usepackage{hyperref}
\usepackage{xurl}
\externaldocument{supplement}

\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\short}{sh}
\DeclareMathOperator{\Ex}{\mathbb{E}}

@@

An additional limitation of the current work and opportunity for further investigation is to more carefully evaluate whether a forecast adds value to existing decision making processes.
In the context of allocation-based decisions, standard procedures might involve extrapolating need based on a current observed data (similar to the `baseline' model presented above), with or without adjustments based on other political or real-world considerations.
For example, in many settings public health stakeholders will synthesize multiple sources of information, e.g. real-time data from a wide variety of quantitative and qualitative sources coupled with expert judgment based on a situational understanding of past and current experience.
The allocation score presented in this work assesses the optimality of the allocation with reference an omniscient view of the future captured by the oracle.
However, what we care about is whether a given forecast adds useful information to an existing decision-making process.
While the scoring procedures as presented do not directly address this question, they could be modified (say, by comparison to a `baseline' model) to quantify the benefit---if any---of using a forecast to inform a specific decision.

We see this work as an initial overture for what we hope will grow to be a large, collaborative body of work more closely coupling applied epidemiological forecasting with public health decision making.
We note that a few papers have begun exploring similar linkages as described in the literature review{\textendash}but we see much room for additional work in this area.
In some situations, individual or ensemble models could be developed to optimize scores that are attuned to a particular decision making setting.
This area is also largely unexplored in the realm of public health to date, with some initial methodological development in econometrics \citep{loaiza-maya_focused_2021}.

### 2023-12-13 alloscore_manuscript/supplement.rnw
a few cosmetic changes

\end{axis}
\end{tikzpicture}
\caption{Shortage functions. $\short^{y_0}(x)$, shown in blue, gives the resource shortage as a function of the level of available resources, $x$, for a fixed value of resource demand $y_0$. $\short_{x_0}(y)$, shown in red, gives the resource shortage as a function of resource demand, $y$, for a fixed value of resource supply $x_0$.}
\label{fig:shortages}
\end{figure}

@@

In section 3 of the manuscript, we used the allocation score to evaluate forecasts of COVID-19 hospitalizations that have been submitted to the COVID-19 Forecast Hub. These forecasts are submitted to the Hub using a set of 23 quantiles of the forecast distribution at the 23 probability levels in the set $\mathcal{T} = \{0.01, 0.025, 0.05, 0.1, 0.15, \ldots, 0.9, 0.95, 0.975, 0.99\}$, which specify a predictive median and the endpoints of central $(1 - \alpha) \times 100\%$ prediction intervals at levels $\alpha = 0.02, 0.05, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9$. For a given week and target date, we use $q_{i,k}$ to denote the submitted quantiles for location $i$ and probability level $\tau_k \in \mathcal{T}$, $k = 1, \ldots, 23$.

>>>>

\end{axis}
\end{tikzpicture}
\caption{Shortage functions. $\mathrm{sh}^{y_0}(x)$, shown in blue, gives the resource shortage as a function of the level of available resources, $x$, for a fixed value of resource demand $y_0$. $\mathrm{sh}_{x_0}(y)$, shown in red, gives the resource shortage as a function of resource demand, $y$, for a fixed value of resource supply $x_0$.}
\label{fig:shortages}
\end{figure}

@@

In section 3 of the manuscript, we used the allocation score to evaluate forecasts of COVID-19 hospitalizations that have been submitted to the COVID-19 Forecast Hub. These forecasts are submitted to the Hub using a set of 23 quantiles of the forecast distribution at the 23 probability levels in the set $\mathcal{T} = \{0.01, 0.025, 0.05, 0.1, 0.15, \ldots, \allowbreak 0.9, 0.95, 0.975, 0.99\}$, which specify a predictive median and the endpoints of central $(1 - \alpha) \times 100\%$ prediction intervals at levels $\alpha = 0.02, 0.05, 0.1, 0.2, \allowbreak 0.3, 0.4, 0.5, 0.6, \allowbreak 0.7, 0.8, 0.9$. For a given week and target date, we use $q_{i,k}$ to denote the submitted quantiles for location $i$ and probability level $\tau_k \in \mathcal{T}$, $k = 1, \ldots, 23$.
